---
title: "Generating figures and analysis for: An applied framework to unlocking multi-angular UAV reflectance data: A case study for classification of plant parameters in corn (Zea mays)"
author: "RH"
date: "2023-02-24"
output:
  html_document:
    df_print: paged
---

# 0 Loading libraries

```{r, echo = FALSE, message=FALSE, include=FALSE}
library(tidyverse)
library(reshape2)
library(arrow)
library(mltools)
library(patchwork)
library(agricolae) # Fishers LSD posthoc

library(pastecs) #stats
library(car) #stats
library(psych) #kruskal wallis
library(stargazer)
```

# 1 Loading reference and classificaton data

```{r, include=FALSE, echo = FALSE}



ref_path <- file.path("D:",
                      "OneDrive - Institut für Zuckerrübenforschung",
                      "03_projects", 
                      "proj_on_uav", 
                      "code_copied", 
                      "on_uav_r_stats",
                      "proc",
                      "ref_data.csv")


class_path <- file.path("D:",
                      "OneDrive - Institut für Zuckerrübenforschung",
                      "03_projects", 
                      "proj_on_uav", 
                      "code_copied", 
                      "on_uav_r_stats",
                      "proc", 
                      "20230127_classif_data.csv")

ref_df <-read_csv(ref_path)
class_df <-read_csv(class_path)

class_df <- select(class_df, -c('...1'))

colnames(class_df) <- c('dates','resolution','parameter', "model", "approaches", "dataset", 
                        "vza_group", "vaa_group", "mean_oa", "sd_oa", 
                        "mean_f1", "sd_f1")

class_df$model[class_df$model == 'RF'] <- 'random_forest'
class_df$model[class_df$model == 'Etra trees'] <- 'extra_trees'

class_df$resolution[class_df$resolution == '1m'] <- '100cm'

class_df$parameter[class_df$parameter == 'chl'] <- 'LCC'
class_df$parameter[class_df$parameter == 'lai'] <- 'LAI'
class_df$parameter[class_df$parameter == 'nbi'] <- 'NBI'
class_df$parameter[class_df$parameter == 'glai'] <- 'GLAI'


class_df$dataset[class_df$dataset == 'All_flight'] <- 'NOO'
class_df$dataset[class_df$dataset == 'Nadir_flight'] <- 'N'

class_df$vza_group[class_df$vza_group == 'mosaic'] <- 'orthomosaic'
class_df$vza_group[class_df$vza_group == 'all'] <- 'all vza'

class_df$vaa_group[class_df$vaa_group == 'mosaic'] <- 'orthomosaic'
class_df$vaa_group[class_df$vaa_group == 'all'] <- 'all vaa'
#class_df$vaa_group[class_df$vaa_group == 'back scattering'] <- 'bs'
#class_df$vaa_group[class_df$vaa_group == 'side scattering'] <- 'ss'
#class_df$vaa_group[class_df$vaa_group == 'forward scattering'] <- 'fs'

class_df$dates <- as.factor(class_df$dates)
class_df$resolution <- as.factor(class_df$resolution)
class_df$parameter <- as.factor(class_df$parameter)
class_df$dataset <- as.factor(class_df$dataset)
class_df$model <- as.factor(class_df$model)
class_df$vza_group <- as.factor(class_df$vza_group)
class_df$vaa_group <- as.factor(class_df$vaa_group)

```


# 2 ANOVA GSD

```{r}

ggplot(class_df, aes(vza_group, mean_f1)) + 
  geom_boxplot(aes(colour = resolution))+
  facet_grid(dates ~ dataset, scales = "free", space = "free")+
  theme(legend.position = "bottom")

#ggplot(class_df, aes(resolution, mean_f1)) + 
#  geom_boxplot()+
#  theme(legend.position = "bottom")

#ggplot(class_df, aes(x=mean_f1)) + geom_histogram()+
#  facet_grid(dates ~ resolution, scales = "free", space = "free")

```

```{r}

kruskal.test(class_df$mean_f1~class_df$resolution)

pairwise.wilcox.test(class_df$mean_f1, class_df$resolution, p.adjust="bonferroni")

```

```{r}
by_gsd <- class_df %>% group_by(resolution)

by_gsd %>% summarise(
  f1 = mean(mean_f1)
)
```

## 2.1 Subsetting for 100cm GSD

```{r}
df_1m <- subset(class_df, resolution == "100cm")

df_1m$mean_f1 <- round(df_1m$mean_f1, 2)

df_1m_lai <- subset(df_1m, parameter == "LAI")
df_1m_glai <- subset(df_1m, parameter == "GLAI")
df_1m_lcc <- subset(df_1m, parameter == "LCC")
df_1m_nbi <- subset(df_1m, parameter == "NBI")
```


```{r}
ggplot(df_1m, aes(vaa_group, mean_f1)) + 
  geom_boxplot(aes(colour = model))+
  facet_grid(dates ~ parameter, scales = "free", space = "free")
```

# 3 ANOVA - Summary of group differences including interactions

```{r}
lai_model <- lm(mean_f1 ~ model + dates + vza_group + vaa_group + dataset + model : dates + model : vza_group + model : vaa_group + dates : vza_group + dates :vaa_group + dataset : model + dataset : dates + dataset : vza_group + dataset : vaa_group, data = df_1m_lai)

glai_model <- lm(mean_f1 ~ model + dates + vza_group + vaa_group + dataset + model : dates + model : vza_group + model : vaa_group + dates : vza_group + dates :vaa_group + dataset : model + dataset : dates + dataset : vza_group + dataset : vaa_group, data = df_1m_glai)

lcc_model <- lm(mean_f1 ~ model + dates + vza_group + vaa_group + dataset + model : dates + model : vza_group + model : vaa_group + dates : vza_group + dates :vaa_group + dataset : model + dataset : dates + dataset : vza_group + dataset : vaa_group, data = df_1m_lcc)


nbi_model <- lm(mean_f1 ~ model + dates + vza_group + vaa_group + dataset + model : dates + model : vza_group + model : vaa_group + dates : vza_group + dates :vaa_group + dataset : model + dataset : dates + dataset : vza_group + dataset : vaa_group, data = df_1m_nbi)
```

```{r}
anova(lai_model)
```
```{r}
anova(glai_model)
```

```{r}
anova(lcc_model)
```

```{r}
anova(nbi_model)
```
We learned that:

  - There is a stark *difference in accuracy between the ET and RF model*
  - There is a stark *difference in accuracy between day 1 and day 2*
  - There is a stark *difference between some of the VZA groups*
  - There is somewhat of a *difference between the VAA groups*
  - There is a *difference between the accuracy when using nadir (N) or NOO data*
  - That there is an *interaction effect between dates and VAA groups*
  - That there is somewhat of an *interaction effect between dates and VZA groups*


## 3.1 Which model performs better

```{r}
ggplot(df_1m, aes(model, mean_f1)) + 
  geom_boxplot()
```
The ET model performs slightly better.

## 3.2 Which day performs better?

```{r}
ggplot(df_1m, aes(dates, mean_f1)) + 
  geom_boxplot()
```

```{r}
kruskal.test(df_1m$mean_f1~df_1m$dates)

pairwise.wilcox.test(class_df$mean_f1, class_df$dates, p.adjust="bonferroni")
```
```{r}
aov_model <- aov(mean_f1 ~ dates, data = df_1m)
anova(aov_model)
print(LSD.test(aov_model,"dates"))
```


The second day performs clearly better.

## 3.3 Which VZA group is best (Day1)?

```{r}

df_1m_d1 <- subset(df_1m, dates == "20200906")


aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_d1)
anova(aov_model)
print(LSD.test(aov_model,"vza_group"))
```

## 3.4 Which VZA group is best (Day2)?

```{r}

df_1m_d2 <- subset(df_1m, dates == "20200907")


aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_d2)
anova(aov_model)
print(LSD.test(aov_model,"vza_group"))
```

## 3.5 Which VAA group is best (Day1)?

```{r}

df_1m_d1 <- subset(df_1m, dates == "20200906")


aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_d1)
anova(aov_model)
print(LSD.test(aov_model,"vaa_group"))
```


## 3.6 Which VAA group is best (Day2)?

```{r}

df_1m_d2 <- subset(df_1m, dates == "20200907")


aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_d2)
anova(aov_model)
print(LSD.test(aov_model,"vaa_group"))
```



## 3.7 Which dataset performs best?

```{r}
ggplot(df_1m, aes(dataset, mean_f1)) + 
  geom_boxplot(aes(colour = vza_group))
```
```{r}
aov_model <- aov(mean_f1 ~ dataset, data = df_1m)
anova(aov_model)
print(LSD.test(aov_model,"dataset"))
```

```{r}
aov_model <- aov(mean_f1 ~ dataset*vza_group, data = df_1m)
anova(aov_model)
print(LSD.test(aov_model,"vza_group"))
```

At a significance level of 0.05, there is no clear difference between the datasets.

## 3.8 Do the leaf parameter accuracies differ between datasets?

### LAI

```{r}
aov_model <- aov(mean_f1 ~ dataset, data = df_1m_lai)

anova(aov_model)

#print(LSD.test(aov_model,"dataset")) 
```

```{r}

df_1m_lai_d1 <- subset(df_1m_lai, dates == "20200906")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_lai_d1)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))

```
```{r}

df_1m_lai_d2 <- subset(df_1m_lai, dates == "20200907")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_lai_d2)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))

```
### GLAI

```{r}
aov_model <- aov(mean_f1 ~ parameter, data = df_1m)

anova(aov_model)

print(LSD.test(aov_model,"parameter")) 
```

```{r}
aov_model <- aov(mean_f1 ~ dataset, data = df_1m_glai)

anova(aov_model)

#print(LSD.test(aov_model,"dataset")) 
```
### LCC

```{r}
df_1m_lcc_d1 <- subset(df_1m_lcc, dates == "20200906")

aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_lcc_d1)

anova(aov_model)

print(LSD.test(aov_model,"vza_group"))
```

```{r}
df_1m_lcc_d2 <- subset(df_1m_lcc, dates == "20200907")

aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_lcc_d2)

anova(aov_model)

print(LSD.test(aov_model,"vza_group"))
```

```{r}
aov_model <- aov(mean_f1 ~ dates, data = df_1m_lcc)

anova(aov_model)

print(LSD.test(aov_model,"dates")) 
```

```{r}
df_1m_lcc_d1 <- subset(df_1m_lcc, dates == "20200906")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_lcc_d1)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))
```
```{r}
df_1m_lcc_d2 <- subset(df_1m_lcc, dates == "20200907")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_lcc_d2)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))
```

```{r}
aov_model <- aov(mean_f1 ~ dataset, data = df_1m_lcc)

anova(aov_model)

#print(LSD.test(aov_model,"dataset")) 
```

### NBI
```{r}
df_1m_nbi_d1 <- subset(df_1m_nbi, dates == "20200906")

aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_nbi_d1)

anova(aov_model)

print(LSD.test(aov_model,"vza_group"))
```

```{r}
df_1m_nbi_d2 <- subset(df_1m_nbi, dates == "20200907")

aov_model <- aov(mean_f1 ~ vza_group, data = df_1m_nbi_d2)

anova(aov_model)

print(LSD.test(aov_model,"vza_group"))
```

```{r}
df_1m_nbi_d1 <- subset(df_1m_nbi, dates == "20200906")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_nbi_d1)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))
```

```{r}
df_1m_nbi_d2 <- subset(df_1m_nbi, dates == "20200907")

aov_model <- aov(mean_f1 ~ vaa_group, data = df_1m_nbi_d2)

anova(aov_model)

print(LSD.test(aov_model,"vaa_group"))
```



```{r}
aov_model <- aov(mean_f1 ~ dates, data = df_1m_nbi)

anova(aov_model)

print(LSD.test(aov_model,"dates")) 
```

```{r}
aov_model <- aov(mean_f1 ~ dataset, data = df_1m_nbi)

anova(aov_model)

print(LSD.test(aov_model,"dataset")) 
```

# 4 Figure 3 - VZA and VAA Distribution

```{r feather}


convert_deg <- function(deg) {
   return (deg %% 360)
}

feather_path <- "D:\\OneDrive - Institut für Zuckerrübenforschung\\03_projects\\proj_on_uav\\code_copied\\on_uav_r_stats\\proc\\python\\main_03\\"

## Load feather and remove 65535 values
df_nadir_d1 <- arrow::read_feather(paste0(feather_path, "on_uav_for_classification_20200906_nadir_flight.feather"))
df_nadir_d1 <- subset(df_nadir_d1, band10 != 65535)

df_all_d1 <- arrow::read_feather(paste0(feather_path, "on_uav_for_classification_20200906_all_flight.feather"))
df_all_d1 <- subset(df_all_d1, band10 != 65535)

df_nadir_d2 <- arrow::read_feather(paste0(feather_path, "on_uav_for_classification_20200907_nadir_flight.feather"))
df_nadir_d2 <- subset(df_nadir_d2, band10 != 65535)

df_all_d2 <- arrow::read_feather(paste0(feather_path, "on_uav_for_classification_20200907_all_flight.feather"))
df_all_d2 <- subset(df_all_d2, band10 != 65535)

## Add dataset type column and date column

df_nadir_d1$dataset <- replicate(nrow(df_nadir_d1), "n")
df_nadir_d1$date <- replicate(nrow(df_nadir_d1), "20200906")

df_all_d1$dataset <- replicate(nrow(df_all_d1), "noo")
df_all_d1$date <- replicate(nrow(df_all_d1), "20200906")

df_nadir_d2$dataset <- replicate(nrow(df_nadir_d2), "n")
df_nadir_d2$date <- replicate(nrow(df_nadir_d2), "20200907")

df_all_d2$dataset <- replicate(nrow(df_all_d2), "noo")
df_all_d2$date <- replicate(nrow(df_all_d2), "20200907")

## Create vza bins

df_nadir_d1$vza_grp <- bin_data(df_nadir_d1$vza, bins=c(0, 12, 17, 21, 35), binType = "explicit")
df_nadir_d2$vza_grp <- bin_data(df_nadir_d2$vza, bins=c(0, 12, 17, 21, 35), binType = "explicit")

df_all_d1$vza_grp <- bin_data(df_all_d1$vza, bins=c(0, 14, 19, 25, 50), binType = "explicit")
df_all_d2$vza_grp <- bin_data(df_all_d2$vza, bins=c(0, 14, 19, 25, 50), binType = "explicit")

df_nadir <- bind_rows(df_nadir_d1, df_nadir_d2)
df_all <- bind_rows(df_all_d1, df_all_d2)

df_nadir$vaa_deg <- convert_deg(df_nadir$vaa)
df_all$vaa_deg <- convert_deg(df_all$vaa)

df_nadir$vaa_grp <- bin_data(df_nadir$vaa_deg, bins=c(0, 60, 120, 240, 300, 360), binType = "explicit")

df_nadir$vaa_grp <- as.character(df_nadir$vaa_grp)

df_nadir$vaa_grp[df_nadir$vaa_grp == '[240, 300)'] <- 'side scattering'
df_nadir$vaa_grp[df_nadir$vaa_grp == '[60, 120)'] <- 'side scattering'

df_nadir$vaa_grp[df_nadir$vaa_grp == '[120, 240)'] <- 'forward scattering'

df_nadir$vaa_grp[df_nadir$vaa_grp == '[300, 360]'] <- 'back scattering'
df_nadir$vaa_grp[df_nadir$vaa_grp == '[0, 60)'] <- 'back scattering'


df_all$vaa_grp <- bin_data(df_all$vaa_deg, bins=c(0, 60, 120, 240, 300, 360), binType = "explicit")

df_all$vaa_grp <- as.character(df_all$vaa_grp)

df_all$vaa_grp[df_all$vaa_grp == '[240, 300)'] <- 'side scattering'
df_all$vaa_grp[df_all$vaa_grp == '[60, 120)'] <- 'side scattering'

df_all$vaa_grp[df_all$vaa_grp == '[120, 240)'] <- 'forward scattering'

df_all$vaa_grp[df_all$vaa_grp == '[300, 360]'] <- 'back scattering'
df_all$vaa_grp[df_all$vaa_grp == '[0, 60)'] <- 'back scattering'

# backscattering (0-60, 300-360), 1 other for forward scattering (120-240), and a third one for side scattering (60-120, 240-300).

```



```{r}
# Exporting camera positions
campos_d1 <- select(df_all_d1, plot, xcam, ycam)
campos_d2 <- select(df_all_d2, plot, xcam, ycam)


write.csv(campos_d1, "campos_d1.csv", row.names=FALSE)
write.csv(campos_d2, "campos_d2.csv", row.names=FALSE)
```


```{r plotdist}
cbPalette <- c("#d8b365", "#5ab4ac", "#D55E00", "#0072B2", "#CC79A7")

p1 <- ggplot(df_nadir, aes(x=vza, fill=date)) + 
  geom_histogram(binwidth = 1) +
  facet_wrap(vaa_grp ~. ) +
  ggtitle("Nadir Flight (N)")+
  xlab("VZA [°]") + ylab("Number of Pixels")+
  #ylim(0, 2000)+
  #annotate("text", x = c(2), y=1800, label = c("a"))+
  #scale_fill_grey()+
  theme_classic()+
  scale_fill_manual(values=cbPalette)+
  theme(legend.position = "none",legend.title=element_blank(), text=element_text(size=16))

  

p2 <- ggplot(df_all, aes(x=vza, fill=date)) + 
  geom_histogram(binwidth = 1) +
  facet_wrap(vaa_grp ~. ) +
  xlab("VZA [°]") + ylab("")+
  ggtitle("All Flights (NOO)")+
  #ylim(0, 3500)+
  #scale_fill_grey()+
  theme_classic()+
  scale_fill_manual(values=cbPalette)+
  theme(text=element_text(size=16))

df_nadir %>%
  filter(!is.na(vza_grp)) %>%
  
ggplot(aes(x=vaa_deg, fill=date)) + 
  geom_histogram(binwidth = 5) +
  facet_wrap(vza_grp ~. ) +
  xlab("VAA [°]") + ylab("Number of Pixels")+
  #ylim(0, 200)+
  #scale_fill_grey()+
  theme_classic()+
  scale_fill_manual(values=cbPalette)+
  theme(legend.position = "none",legend.title=element_blank(), text=element_text(size=16)) -> p3

df_all %>%
  filter(!is.na(vza_grp)) %>%

ggplot(aes(x=vaa_deg, fill=date)) + 
  geom_histogram(binwidth = 5) +
  xlab("VAA [°]") + ylab("")+
  facet_wrap(vza_grp ~. )+
  #ylim(0, 400)+
  #scale_fill_grey()+
  theme_classic()+
  scale_fill_manual(values=cbPalette)+
  theme(text=element_text(size=16)) -> p4

p1 + p2 + p3 + p4 + 
  plot_layout(ncol = 2, guides = "collect") + 
  plot_annotation(tag_levels = 'a')

out <- "D:\\OneDrive - Institut für Zuckerrübenforschung\\03_projects\\proj_on_uav\\docs_copied\\manuscript\\final\\prag\\majorrev\\fig3_vzavaa_dist\\"

ggsave(paste0(out, "fig3_vza_vaa_dist_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)

```

# 5 Figure 4 - Pairplot


## 5.1 Reshaping and cleaning reference data for boxplots

```{r}
colnames(ref_df) <- c('plot','LAI','GLAI', "LCC", "NBI")


ref_melt_glai <- melt(select(ref_df, plot, GLAI), id=c("plot")) 
ref_melt_glai$plot <- as.factor(ref_melt_glai$plot)
ref_melt_lai <- melt(select(ref_df, plot, LAI), id=c("plot"))
ref_melt_lai$plot <- as.factor(ref_melt_lai$plot)
ref_melt_lcc <- melt(select(ref_df, plot, LCC), id=c("plot"))
ref_melt_lcc$plot <- as.factor(ref_melt_lcc$plot)
ref_melt_nbi <- melt(select(ref_df, plot, NBI), id=c("plot")) 
ref_melt_nbi$plot <- as.factor(ref_melt_nbi$plot)

stargazer(data.frame(ref_df)[c("LAI", "GLAI", "LCC", "NBI")],type="text",title="Summary Statistics", out="plant_params.txt")
```
## 5.2 Plotting pairplot 
```{r}

library(GGally)

ggpairs(ref_df, columns = 2:5)

out <- "C:\\Users\\heim\\OneDrive - Institut für Zuckerrübenforschung\\projects\\proj_on_uav\\docs\\manuscript\\final\\figures\\fig4_pairplot\\"

ggsave(paste0(out, "fig4_pairplot.png"), width = 30, height = 20, unit = "cm", dpi = 300)
```

# 6 Classification Results

## 6.1 LAI

```{r}
df_1m_lai_et <- subset(df_1m_lai, model == "extra_trees")

df_1m_lai_et_nadir <- subset(df_1m_lai_et, dataset == "N")
df_1m_lai_et_noo <- subset(df_1m_lai_et, dataset == "NOO")
```

```{r}
df_1m_lai_et_nadir$vaa_group2 = factor(df_1m_lai_et_nadir$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))
df_1m_lai_et_noo$vaa_group2 = factor(df_1m_lai_et_noo$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))

plai_nadir <- ggplot(df_1m_lai_et_nadir, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  scale_y_continuous(breaks=seq(from = 0.6, to = 1, by = 0.1), limits=c(0.6,1))+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="a - LAI | ET | NADIR")+
  #scale_fill_grey()+
  theme_classic()+
  #scale_fill_manual(values=cbPalette)+
  scale_color_manual(values = cbPalette)+
  theme(text=element_text(size=16))

plai_all <- ggplot(df_1m_lai_et_noo, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  scale_y_continuous(breaks=seq(from = 0.6, to = 1, by = 0.1), limits=c(0.6,1))+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="b - LAI | ET | NOO")+
  #scale_fill_grey()+
  theme_classic()+
  #scale_fill_manual(values=cbPalette)+
  scale_color_manual(values = cbPalette)+
  theme(text=element_text(size=16))

plai_nadir + plai_all + plot_layout(ncol = 1, guides = "collect") & theme(legend.position = 'bottom')

out <- "D:\\OneDrive - Institut für Zuckerrübenforschung\\03_projects\\proj_on_uav\\docs_copied\\manuscript\\final\\prag\\majorrev\\fig4_classif\\"

ggsave(paste0(out, "fig5_lai_classif_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)
```

## 6.2 GLAI

```{r}
df_1m_glai_et <- subset(df_1m_glai, model == "extra_trees")

df_1m_glai_et_nadir <- subset(df_1m_glai_et, dataset == "N")
df_1m_glai_et_noo <- subset(df_1m_glai_et, dataset == "NOO")

```

```{r}
df_1m_glai_et_nadir$vaa_group2 = factor(df_1m_glai_et_nadir$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))
df_1m_glai_et_noo$vaa_group2 = factor(df_1m_glai_et_noo$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))

pglai_nadir <- ggplot(df_1m_glai_et_nadir, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), size = 2.5)+
  #geom_jitter(aes(shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  scale_y_continuous(breaks=seq(from = 0.6, to = 1, by = 0.1), limits=c(0.6,1))+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title=" c - GLAI | ET | NADIR")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

pglai_all <- ggplot(df_1m_glai_et_noo, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), size = 2.5)+
  #geom_jitter(aes(shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  scale_y_continuous(breaks=seq(from = 0.6, to = 1, by = 0.1), limits=c(0.6,1))+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="d - GLAI | ET | NOO")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

pglai_nadir + pglai_all + plot_layout(ncol = 1, guides = "collect") & theme(legend.position = 'bottom')

ggsave(paste0(out, "fig5_glai_classif_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)
```



## 6.3 LCC

```{r}
df_1m_lcc_et <- subset(df_1m_lcc, model == "extra_trees")

df_1m_lcc_et_nadir <- subset(df_1m_lcc_et, dataset == "N")
df_1m_lcc_et_noo <- subset(df_1m_lcc_et, dataset == "NOO")

```

```{r}
df_1m_lcc_et_nadir$vaa_group2 = factor(df_1m_lcc_et_nadir$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))
df_1m_lcc_et_noo$vaa_group2 = factor(df_1m_lcc_et_noo$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))

plcc_nadir <-ggplot(df_1m_lcc_et_nadir, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="a - LCC | ET | NADIR")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

plcc_all <-ggplot(df_1m_lcc_et_noo, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = TRUE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="b - LCC | ET | NOO")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

plcc_nadir + plcc_all + plot_layout(ncol = 1, guides = "collect") & theme(legend.position = 'bottom')

#out <- "C:\\Users\\heim\\OneDrive - Institut für Zuckerrübenforschung\\projects\\proj_on_uav\\docs\\manuscript\\final\\figures\\fig6_lcc_nbi_classification\\"

ggsave(paste0(out, "fig6_lcc_classif_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)
```

## 6.4 NBI

```{r}
df_1m_nbi_et <- subset(df_1m_nbi, model == "extra_trees")

df_1m_nbi_et_nadir <- subset(df_1m_nbi_et, dataset == "N")
df_1m_nbi_et_noo <- subset(df_1m_nbi_et, dataset == "NOO")

```

```{r}
df_1m_nbi_et_nadir$vaa_group2 = factor(df_1m_nbi_et_nadir$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))
df_1m_nbi_et_noo$vaa_group2 = factor(df_1m_nbi_et_noo$vaa_group, levels=c('orthomosaic','all vaa','forward scattering','back scattering', 'side scattering'))

pnbi_nadir <- ggplot(df_1m_nbi_et_nadir, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = FALSE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="a - NBI | ET | NADIR")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

pnbi_all <- ggplot(df_1m_nbi_et_noo, aes(vza_group, mean_f1, label=mean_f1)) + 
  geom_point(aes(color = dates, shape = dates), alpha = 0.5, size = 2.5)+
  xlab("VZA Group [°]") + ylab("Accuracy [f1]")+
  geom_text(hjust=-0.4, vjust=0.5, size=5, check_overlap = FALSE)+
  facet_grid(. ~ vaa_group2 , scales = "free", space = "free")+
  labs(title="b - NBI | ET | NOO")+
  #scale_fill_grey()+
  scale_color_manual(values = cbPalette)+
  theme_classic()+
  theme(text=element_text(size=16))

pnbi_nadir + pnbi_all + plot_layout(ncol = 1, guides = "collect") & theme(legend.position = 'bottom')

ggsave(paste0(out, "fig6_nbi_classif_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)
```

## 6.5 Listing f1-scores


```{r}
by_vza <- df_1m %>% group_by(parameter, vza_group, dataset)

by_vza %>% summarise(
  f1 = mean(mean_f1)
)
```

#7 Feature importance


```{r}
fi_path <- file.path("D:",
                      "OneDrive - Institut für Zuckerrübenforschung",
                      "03_projects", 
                      "proj_on_uav", 
                      "code_copied", 
                      "on_uav_r_stats",
                      "proc", 
                      "20230224_on_uav_feature_importance.csv")

fi_df <- read_csv(fi_path)

colnames(fi_df) <- c('id', 'dates','resolution','parameter', "model", "approaches", "dataset", 
                        "vza_group", "vaa_group", "blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842")

fi_df$model[fi_df$model == 'RF'] <- 'random_forest'
fi_df$model[fi_df$model == 'Etra trees'] <- 'extra_trees'

fi_df$resolution[fi_df$resolution == '1m'] <- '100cm'

fi_df$parameter[fi_df$parameter == 'chl'] <- 'LCC'
fi_df$parameter[fi_df$parameter == 'nbi'] <- 'NBI'
fi_df$parameter[fi_df$parameter == 'lai'] <- 'LAI'
fi_df$parameter[fi_df$parameter == 'glai'] <- 'GLAI'

fi_df$dataset[fi_df$dataset == 'All_flight'] <- 'NOO'
fi_df$dataset[fi_df$dataset == 'Nadir_flight'] <- 'N'

fi_df$vza_group[fi_df$vza_group == 'mosaic'] <- 'orthomosaic'
fi_df$vza_group[fi_df$vza_group == 'all'] <- 'all vza'

fi_df$vaa_group[fi_df$vaa_group == 'mosaic'] <- 'orthomosaic'
fi_df$vaa_group[fi_df$vaa_group == 'all'] <- 'all vaa'
#fi_df$vaa_group[fi_df$vaa_group == 'back scattering'] <- 'bs'
#fi_df$vaa_group[fi_df$vaa_group == 'side scattering'] <- 'ss'
#fi_df$vaa_group[fi_df$vaa_group == 'forward scattering'] <- 'fs'
```

```{r}
fi_df <- subset(fi_df, model == "extra_trees")

df_fi_lai <- subset(fi_df, parameter == "LAI")
df_fi_glai <- subset(fi_df, parameter == "GLAI")
df_fi_lcc <- subset(fi_df, parameter == "LCC")
df_fi_nbi <- subset(fi_df, parameter == "NBI")
```


```{r}
df_melt_fi <- melt(fi_df, id.vars = c("dates", "parameter", 
"model", "approaches", "dataset", "vza_group", "vaa_group"), measure.vars = c("blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842"), variable.name = "bands", value.name = "rel_importance")

df_melt_fi_lai <- melt(df_fi_lai, id.vars = c("dates", "parameter", 
"model", "approaches", "dataset", "vza_group", "vaa_group"), measure.vars = c("blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842"), variable.name = "bands", value.name = "rel_importance")

df_melt_fi_glai <- melt(df_fi_glai, id.vars = c("dates", "parameter", 
"model", "approaches", "dataset", "vza_group", "vaa_group"), measure.vars = c("blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842"), variable.name = "bands", value.name = "rel_importance")

df_melt_fi_lcc <- melt(df_fi_lcc, id.vars = c("dates", "parameter", 
"model", "approaches", "dataset", "vza_group", "vaa_group"), measure.vars = c("blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842"), variable.name = "bands", value.name = "rel_importance")

df_melt_fi_nbi <- melt(df_fi_nbi, id.vars = c("dates", "parameter", 
"model", "approaches", "dataset", "vza_group", "vaa_group"), measure.vars = c("blue444", "blue475", "green531", "green560", "red650", "red668", "re705", "re717", "re740", "nir842"), variable.name = "bands", value.name = "rel_importance")
```

```{r}

df_fi_noo <- subset(df_melt_fi, dataset == "NOO" & dates == "20200906")
df_fi_n <- subset(df_melt_fi, dataset == "N" & dates == "20200906")

df_fi_noo_2 <- subset(df_melt_fi, dataset == "NOO" & dates == "20200907")
df_fi_n_2 <- subset(df_melt_fi, dataset == "N" & dates == "20200907")

ggplot(df_fi_noo, aes(x = bands, y = rel_importance, fill = parameter, width = 0.5)) +
  geom_col(position="dodge")+
  scale_fill_manual(values = cbPalette)+
  labs(y="Relative Importance", x="", title = "NOO | ET | 20200906")+
  facet_wrap(vza_group ~ vaa_group)+
  #scale_fill_grey()+
  theme_classic()+
  theme(text=element_text(size=16), legend.title=element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

out <- "D:\\OneDrive - Institut für Zuckerrübenforschung\\03_projects\\proj_on_uav\\docs_copied\\manuscript\\final\\prag\\majorrev\\fig6_importance\\"

ggsave(paste0(out, "s16_feature_noo_et_d1_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)

ggplot(df_fi_n, aes(x = bands, y = rel_importance, fill = parameter, width = 0.5)) +
  geom_col(position="dodge")+
  scale_fill_manual(values= cbPalette)+
  #theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y="Relative Importance", x="", title = "N | ET | 20200906")+
  facet_wrap(vza_group ~ vaa_group)+
  #theme(legend.title=element_blank())+
  #scale_fill_grey()+
  theme_classic()+
  theme(text=element_text(size=16), legend.title=element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(paste0(out, "fig7_feature_n_et_d1_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)


ggplot(df_fi_noo_2, aes(x = bands, y = rel_importance, fill = parameter, width = 0.5)) +
  geom_col(position="dodge")+
  scale_fill_manual(values = cbPalette)+
  #theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y="Relative Importance", x="", title = "NOO | ET | 20200907")+
  facet_wrap(vza_group ~ vaa_group)+
  #theme(legend.title=element_blank())+
  #scale_fill_grey()+
  theme_classic()+
  theme(text=element_text(size=16), legend.title=element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

#out <- "C:\\Users\\heim\\OneDrive - Institut für Zuckerrübenforschung\\projects\\proj_on_uav\\docs\\manuscript\\final\\figures\\fig8_rel_feature_n_day2\\"

ggsave(paste0(out, "s17_feature_noo_et_d2_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)

ggplot(df_fi_n_2, aes(x = bands, y = rel_importance, fill = parameter, width = 0.5)) +
  geom_col(position="dodge")+
  scale_fill_manual(values = cbPalette)+
  #theme( axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(y="Relative Importance", x="", title = "N | ET | 20200907")+
  facet_wrap(vza_group ~ vaa_group)+
  #theme(legend.title=element_blank())+
  #scale_fill_grey()+
  theme_classic()+
  theme(text=element_text(size=16), legend.title=element_blank(), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggsave(paste0(out, "fig8_feature_n_et_d2_color.png"), width = 40, height = 20, unit = "cm", dpi = 600)
```

# 8 Plotting spectra


```{r}

#NADIR

sel <- select(df_nadir, plot, vza_grp,  vaa_grp, date, band1, band2, band3, band4, band5, band6, band7, band8, band9, band10)

colnames(sel) <- c("plot", "vza_grp", "vaa_grp", "date", "444", "475", "531", "560", "650", "668", "705", "717", "740", "842")

df_melt <- melt(sel, id.vars = c("plot", 
"vza_grp", "vaa_grp", "date"), variable.name = "wavelength", value.name = "reflectance")

df_melt$vza_group <- ntile(df_melt$vza, 5)

df_melt$reflectance <- df_melt$reflectance/65535

df_melt$wavelength <- as.numeric(as.character(df_melt$wavelength))
df_melt$vaa_grp <- as.factor(df_melt$vaa_grp)




by_vzag <- df_melt %>% group_by(vza_grp, wavelength, plot, date)

by_vzag %>% summarise(
  reflectance = mean(reflectance)) -> df_reflec_nadir


#ALL



sel <- select(df_all, plot, vza_grp,  vaa_grp, date, band1, band2, band3, band4, band5, band6, band7, band8, band9, band10)

colnames(sel) <- c("plot", "vza_grp", "vaa_grp", "date", "444", "475", "531", "560", "650", "668", "705", "717", "740", "842")

df_melt <- melt(sel, id.vars = c("plot", 
"vza_grp", "vaa_grp", "date"), variable.name = "wavelength", value.name = "reflectance")

df_melt$vza_group <- ntile(df_melt$vza, 5)

df_melt$reflectance <- df_melt$reflectance/65535

df_melt$wavelength <- as.numeric(as.character(df_melt$wavelength))
df_melt$vaa_grp <- as.factor(df_melt$vaa_grp)




by_vzag <- df_melt %>% group_by(vza_grp, wavelength, plot, date)

by_vzag %>% summarise(
  reflectance = mean(reflectance)) -> df_reflec_all
```

```{r}

#out = "C:\\Users\\heim\\OneDrive - Institut für Zuckerrübenforschung\\projects\\proj_on_uav\\docs\\manuscript\\final\\figures\\s3_6_spectra\\"

df_reflec_nadir %>%
  filter(!is.na(vza_grp)) %>%
  
ggplot( aes(wavelength, reflectance, colour = vza_grp)) +
  geom_line(aes(colour=vza_grp), linewidth = 0.1)+
  geom_point(size = 0.5)+
  scale_x_continuous(breaks = seq(400, 900, 100))+
  facet_wrap(plot ~ date)+
  ggtitle("spectra_nadir_vza")

ggsave(filename = paste0(out, "spectra_nadir_vza.png"), width = 
         30, height = 20, dpi = 600, units = "cm", device='png')

df_reflec_all %>%
  filter(!is.na(vza_grp)) %>%
  
ggplot( aes(wavelength, reflectance, colour = vza_grp)) +
  geom_line(aes(colour=vza_grp), linewidth = 0.1)+
  geom_point(size = 0.5)+
  scale_x_continuous(breaks = seq(400, 900, 100))+
  facet_wrap(plot ~ date)+
  ggtitle("spectra_all_vza")

ggsave(filename = paste0(out, "spectra_all_vza.png"), width = 
         30, height = 20, dpi = 600, units = "cm", device='png')

```

```{r}
by_vaag <- df_melt %>% group_by(vaa_grp, wavelength, plot, date)

by_vaag %>% summarise(
  reflectance = mean(reflectance)) -> df_reflec_nadir


by_vaag <- df_melt %>% group_by(vaa_grp, wavelength, plot, date)

by_vaag %>% summarise(
  reflectance = mean(reflectance)) -> df_reflec_all



df_reflec_nadir %>%
  filter(!is.na(vaa_grp)) %>%
  
ggplot( aes(wavelength, reflectance, colour = vaa_grp)) +
  geom_line(aes(colour=vaa_grp), linewidth = 0.1)+
  geom_point(size = 0.5)+
  scale_x_continuous(breaks = seq(400, 900, 100))+
  facet_wrap(plot ~ date)+
  ggtitle("spectra_nadir_vaa")

ggsave(filename = paste0(out, "spectra_nadir_vaa.png"), width = 
         30, height = 20, dpi = 600, units = "cm", device='png')

df_reflec_all %>%
  filter(!is.na(vaa_grp)) %>%
  
ggplot( aes(wavelength, reflectance, colour = vaa_grp)) +
  geom_line(aes(colour=vaa_grp), linewidth = 0.1)+
  geom_point(size = 0.5)+
  scale_x_continuous(breaks = seq(400, 900, 100))+
  facet_wrap(plot ~ date)+
  ggtitle("spectra_all_vaa")

ggsave(filename = paste0(out, "spectra_all_vaa.png"), width = 
         30, height = 20, dpi = 600, units = "cm", device='png')
```


# 9 Analyse camera tilt

```{r}
fl1_d1 <- read_delim("20200906_bot_corn_comb_cameras_fl1.csv", delim=";")
fl1_d1$date <- replicate(nrow(fl1_d1), "20200906")
fl1_d1$flight <- replicate(nrow(fl1_d1), "1")

fl2_d1 <- read_delim("20200906_bot_corn_comb_cameras_fl2.csv", delim=";")
fl2_d1$date <- replicate(nrow(fl2_d1), "20200906")
fl2_d1$flight <- replicate(nrow(fl2_d1), "2")

fl3_d1 <- read_delim("20200906_bot_corn_comb_cameras_fl3.csv", delim=";")
fl3_d1$date <- replicate(nrow(fl3_d1), "20200906")
fl3_d1$flight <- replicate(nrow(fl3_d1), "3")

fl1_d2 <- read_delim("20200907_bot_corn_comb_cameras_fl1.csv", delim=";")
fl1_d2$date <- replicate(nrow(fl1_d2), "20200907")
fl1_d2$flight <- replicate(nrow(fl1_d2), "1")

fl2_d2 <- read_delim("20200907_bot_corn_comb_cameras_fl2.csv", delim=";")
fl2_d2$date <- replicate(nrow(fl2_d2), "20200907")
fl2_d2$flight <- replicate(nrow(fl2_d2), "2")

fl3_d2 <- read_delim("20200907_bot_corn_comb_cameras_fl3.csv", delim=";")
fl3_d2$date <- replicate(nrow(fl3_d2), "20200907")
fl3_d2$flight <- replicate(nrow(fl3_d2), "3")

df_fl <- rbind(fl1_d1, fl2_d1, fl3_d1, fl1_d2, fl2_d2, fl3_d2)

```
```{r}
ggplot(df_fl, aes(x=PhotoID, y=Omega, color=flight)) +
  geom_point() +
  facet_wrap(date ~ .)+
  theme(axis.text.x=element_blank(), #remove x axis labels
          axis.ticks.x=element_blank(), #remove x axis ticks
          )
```

